This is an example of article title

### 2019-06-22 paper/paper.tex
versions, and gcc re-run

\subsection{Other platforms}
A final experiment was carried out with different programming languages in the same machine and with Julia in different machines, to provide more context. Table~\ref{tab:bench-cxx} displays statistics collected from Julia, Python and C++ programs. For the case of Python the measurements obtained by calling the function through PyCall were better than using the native Python shell, therefore the best value was kept. Results obtained for C++ with Julia inter-operation using {\tt Cxx.jl} were slightly worse than native, thus discarded. While Numpy was almost as fast as Julia, no reason could be found for the dismal performance of the C++ standard library.

\begin{table}[h]
\tabcolsep11pt
\tbl{Sorting arrays of 8k and 1M {\tt UInt32} elements in different software platforms.}{
\begin{tabular}{|l|r|r|}\hline
Method & 8k & 1M\\\hline
\chipsort & 172.35 $\mu$s & 35.28 ms\\\hline
Julia standard & 345.46 $\mu$s & 68.39 ms\\\hline
Numpy via PyCall & 369.50 $\mu$s & 70.01 ms\\\hline
C++ {\tt std::qsort} & 788.59 $\mu$s & 147.37 ms\\\hline
C++ {\tt std::sort} & 1,207.23 $\mu$s & 224.71 ms\\\hline
\end{tabular}}
\label{tab:bench-cxx}
\end{table}

>>>>

\subsection{Other platforms}
One last experiment was carried out with different programming languages in the same machine and with Julia in different machines, to provide more context. Table~\ref{tab:bench-cxx} displays statistics collected from Julia, Python and C++ programs. Versions utilized were Julia 1.3.0-DEV.431, Python 3.6.8 with Numpy 1.14.3 and GCC 8.3.0 with libstdc++ 6.0.25 on a Ubuntu 18.04 system. For the case of Python the measurements obtained by calling the function through PyCall were better than using the native Python shell, therefore the best value was kept. Results obtained for C++ with Julia inter-operation using {\tt Cxx.jl} were slightly worse than native, thus discarded. While Numpy was almost as fast as Julia, no reason could be found for the dismal performance of the C++ standard library.

\begin{table}[h]
\tabcolsep11pt
\tbl{Sorting arrays of 8k and 1M {\tt UInt32} elements in different software platforms.}{
\begin{tabular}{|l|r|r|}\hline
Method & 8k & 1M\\\hline
\chipsort & 172.35 $\mu$s & 35.28 ms\\\hline
Julia standard & 337.03 $\mu$s & 68.39 ms\\\hline
Numpy via PyCall & 354.55 $\mu$s & 70.01 ms\\\hline
C++ {\tt std::qsort} & 770.93 $\mu$s & 143.48 ms\\\hline
C++ {\tt std::sort} & 1,177.54 $\mu$s & 221.27 ms\\\hline
\end{tabular}}
\label{tab:bench-cxx}
\end{table}
